%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
%   \cventry
%     {Front-end developer} % Job title
%     {Freelancing} % Organization
%     {Stockholm, Sweden} % Location
%     {May. 2022 - Present} % Date(s)
%     {
%       \begin{cvitems} % Description(s) of tasks/responsibilities
%         \item {Designed and coded web pages for web3 projects such as landing page for NFT or NFT collection viewer. }
%         \item {Developed an language learning app as a personal project with future plans of introducing paid plans}
%         \item {Developed npm package for scraping translations from wiktionary.org}
%       \end{cvitems}
%     }
%---------------------------------------------------------
  \cventry
    {Maintenance Technician} % Job title
    {Ocado Engineering} % Organization
    {Stockholm, Sweden} % Location
    {Aug. 2021 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Diagnosed and fixed most challenging issues on 500 series bots.}
        \item {Performed site acceptance tests on a big part of the current bot fleet on site.}
        \item {Recognized root cause for common errors occurring on bots during the operation.}
        \item {Managed to resolve network-related problems on bots with refurbished BotPC installed}
        \item {Studied electrical and mechanical solutions on bots to deliver the best quality service and resolve the most complex problems.}
      \end{cvitems}
    }
    
    %---------------------------------------------------------
  \cventry
    {Mechanic} % Job title
    {Bolt} % Organization
    {Stockholm, Sweden} % Location
    {Apr. 2021 - Aug. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      \item{Diagnosed and fixed electric vehicles.}
      \item{Performed workshop repairs involving drilling, milling and tapping.}
      \end{cvitems}
    }
    
  \cventry
    {Junior Design Engineer {\enskip\cdotp\enskip} Mechanical Engineering Intern} % Job title
    {TechnipFMC} % Organization
    {Kraków, Poland} % Location
    {Oct. 2018 - Oct. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      \item{Developed hydraulic rerouting device controlled by a remotely operated underwater vehicle (ROV).}
      \item{Created CAD documentation for a new series of high-pressure hydraulic couplers.}
      \item{Designed and maintained documentation of hydraulic control systems equipment.}
      \item{Supported product engineer with the development and design of the universal hydraulic connector.}
      \end{cvitems}
    }
    
      \cventry
    {Mechanical Engineering Intern} % Job title
    {BWI Poland Technologies} % Organization
    {Kraków, Poland} % Location
    {Jul. 2018 - Sep. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      \item{Designed improvements for suspension testing machines.}
      \item{Analyzed data from testing machines with Python and Pandas library}
      \item{Managed and maintained a fleet of Raspberry Pis used for sensor data acquisition and displaying machine status information}
      \item{Created Linux Bash scripts to automate the proper startup of bespoke software after Raspberry Pi reboot.}
      \item{Designed fixtures for mounting vehicle suspension on testing machines.}
      \end{cvitems}
    }
%---------------------------------------------------------
\end{cventries}
